\section{Specific Aim 1: Scaleablility and Security}
EyeWire game had over 200,000 users, so our solution needs to scale well. 
We will address 2 key challenges:
\begin{itemize}
\item data management, handling large datasets, distributed computing 
\begin{itemize}
\item need to learn how to use Amazon, spark, distributed computing. Resources at the eScience institute will help. 
\item learn how to connect to amazon turk for paid incentive, zooniverse for free
\end{itemize}
\item serving piece-wise "chunks" of data rather than the whole dataset. This preserves privacy if the data is not open, and reduces the fatigue of users. Need to serve intelligently to figure out which pieces to serve next.
\item show different views: axial, coronal, sagittal
\begin{itemize}
\item different datasets will need to be chunked differently. Lesions need all 3 slices view but brain mask editing, only 1. Needs to be user-specified, to answer the question "how much chunking is necessary for this application"
\end{itemize}
\end{itemize}

\section{Specific Aim 2: Learning by Example}

Address 2 challenges:
\begin{itemize}
\item resolving user input to create a final image, based on training data
\begin{itemize}
\item create a probability image weighted by how well each user did on the training data
\item joint fusion strategy?
\end{itemize}
\item predicting regions of variability to serve more efficiently
\begin{itemize}
\item can we predict which voxels are "controversial" and only show those?
\end{itemize}
\end{itemize}

\section{Specific Aim 3: Training and Gamification}
\begin{itemize}
\item training: how frequently does training data need to be used
\begin{itemize}
\item need to signal to users that this is being verified, avoid malicious users, increase time and care spent on task
\item also keep track of time spent on task. If many voxels were erased, were they erased quickly or slowly. 
\end{itemize}
\item UI edit, gamify
\begin{itemize}
\item already have mindcontrol platform to do editing
\item give badges relative to volume of voxels edited, reward training with points for feedback
\item use amazon turk's api rather than the turk platform itself. 
\end{itemize}
\end{itemize}