\section{Specific Aim 1: Scaleable and Secure Micro-Tasks}

This aim will address two key challenges: 1) Partitioning 3D data into microtasks that keep data private, 2) serving micro-tasks at scale. While there exists many large-scale open-source data collection efforts, many datasets are kept private within research institutions due to  IRB restrictions, so presenting a full 3D MRI volume to the public would be a violation. Serving smaller "chunks" of data serves two purposes: it allows us to keep data private and reduces the fatigue of non-experts, which enables us to engage a larger user-base. A scaleable server will be implemented on the Amazon cloud, with an API that allows researchers to upload MRI slices to the server database. Researchers will be asked to provide the following to the API: 1) an initial segmentation file from an automated algorithm 2) any original images (T1, T2, PD) that  users need to properly edit the segmentation 3) to specify how the images should be sliced (including the slicing plane and the number of slices) into microtasks. Additionally, researchers must provide a validation dataset, which includes "correctly" segmented images, which will be used to train non-experts in aim 3.

EyeWire game had over 200,000 users, so our solution needs to scale well. 
We will address 2 key challenges:
\begin{itemize}
\item data management, handling large datasets, distributed computing 
\begin{itemize}
\item need to learn how to use Amazon, spark, distributed computing. Resources at the eScience institute will help. 
\item learn how to connect to amazon turk for paid incentive, zooniverse for free
\end{itemize}
\item serving piece-wise "chunks" of data rather than the whole dataset. This preserves privacy if the data is not open, and reduces the fatigue of users. Need to serve intelligently to figure out which pieces to serve next.
\item show different views: axial, coronal, sagittal
\begin{itemize}
\item different datasets will need to be chunked differently. Lesions need all 3 slices view but brain mask editing, only 1. Needs to be user-specified, to answer the question "how much chunking is necessary for this application"
\end{itemize}
\end{itemize}