

\subsubsection*{Specific Aim 3: Training and Gamification}

The difficulty of manual neuroimaging segmentation depends on the contrast of the image and the difficulty of locating the structure by with minimal neuroanatomy knowledge. An example of an easy task would be segmenting brain tissue from non-brain tissue, whereas a more difficult task would be the segmentation of multiple sclerosis lesions. This aim will address the simple and challenging use cases through varying levels of training and rewards. A web application will be developed that hooks into the server developed in aim 1. The app will include an in-browser brain editor (similar to the Mindcontrol application \cite{keshavan2016mindcontrol}), a reward structure and a scoreboard for the top users, and an optional link to the Amazon Turk engine, where users can be paid (in micro-payments) for completing micro-tasks. Initially, the user will only be presented with training tasks until they reach an adequate accuracy score. Next, the training tasks will be interspersed with new tasks, and the frequency of training tasks will increase based on the researcher's specification of task difficulty. The reward structure will be based on 1) how well the user edits training data 2) how well the user matches with other users 3) how many voxels are edited by the user. The time spent on the task along with the number of edited voxels, will also be used to validate whether or not the user completed the task with some thought. For example, a user's score would be penalized if a large number of voxels were edited too quickly for a difficult task. I plan to collaborate with the data visualization experts at the eScience institute to build an intuitive, fun, and beautiful crowd-sourcing user interface.